%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\def \papersize {a4paper}
\documentclass[12pt,\papersize]{extarticle}
% extarticle is like article but can handle 8pt, 9pt, 10pt, 11pt, 12pt, 14pt, 17pt, and 20pt text

%Mindreading and Joint Action: Philosophical Tools 
%(Fall 2012-3, PhD Elective)
%lecturer: S. Butterfill

\def \ititle {Origins of Mind: Philosophical Issues in Cognitive Development}
\def \isubtitle {}
\def \iauthor {Warwick, Autumn 2013-4, MA and undergrduate}
\def \iemail{s.butterfill@warwick.ac.uk}
%for anonymous submisison
%\def \iauthor {}
%\def \iemail{}
%\date{}

\input{$HOME/Documents/submissions/preamble_steve_paper3}

%avoid overhang
\tolerance=5000


\begin{document}

\setlength\footnotesep{1em}

\bibliographystyle{newapa} %apalike

%these two lines are for anonymous submission --- they remove author and date
%but don't forget to remove defs above as well --- otherwise it will be in the metadata
%\author{}
%\date{}


\maketitle
%\tableofcontents
%
%\begin{abstract}
%\noindent
%***
%\ 
%
%\end{abstract}




\section{Short description}
How do humans come to know about objects, causes, words, numbers, colours, actions and minds?  We will attempt to answer this question using a range of conceptual tools from philosophy to examine puzzles arising from some recent scientific breakthroughs.  The question, which goes back to Plato or earlier, is challenging because it requires us to consider minds where knowledge is neither clearly present nor obviously absent. This is challenging because, as Donald Davidson observes, ‘[w]e have many vocabularies for describing nature when we regard it as mindless, and we have a mentalistic vocabulary for describing thought and intentional action; what we lack is a way of describing what is in between’ (\citeyear[p.\ 11]{Davidson:1999ju}).  To understand the emergence of knowledge we need to investigate what is in between mindless nature and the sorts of cognition captured by commonsense psychological notions.  


%Mindreading and joint action will initially be treated as separate topics.
%Later the course will examine requirements for mindreading in enabling joint action and roles of joint action in enabling mindreading.


%%
%%
%%decomposing mindreading (and joint action) into component processes 
%%
%%in something like that 
%%
%%
%%	examine the construction of
%%	 a framework for understanding mindreading and joint action 
%%	 from first principles.
%%
%%
%Mindreading is 
%	the process of 
%	identifying mental states and actions 
%	as the mental states and actions 	of a particular subject 
%	on the basis, ultimately, of bodily movements and their absence,
%somewhat as reading is the process of identifying propositions on the basis of inscriptions.
%The problem is that we understand almost nothing about mindreading,  despite some groundbreaking discoveries. 
%(And similarly for joint action.)
%Contrast actual reading.
%Reading has been decomposed into orthographic, lexical, syntactic, semantic and pragmatic components.
%There is much research on these components and their interactions. 
%By contrast, mindreading is usually conceived as a single huge jump from observed bodily movements to ascriptions of mental states. 
%This and other considerations suggest that we don't adequately understand what mindreading is.
%
	
Questions arising include:
%
\begin{itemize}
%
\item [\emph{Action}] Does identifying an action as such necessarily involve representing an intention?
%
\item [\emph{Holism}] Could there be mindreaders who can identify intentions and knowledge states but not beliefs?
%
\item [\emph{Modularity}] If mindreading is modular (or  automatic), what can we infer about the representations and processes it involves?
%
\item [\emph{Tracking}] What could someone represent that would enable her, perhaps within limits, to track another's mental states?
%
\item [\emph{Evidential basis}] What evidence could in principle support the ascription of a particular belief to a given subject, and how does the evidence support the ascription?
%
\item [\emph{Objectivity}] Could there be mindreaders who are able to identify beliefs despite not understanding what it is for a belief to be true or false? 
%
\item [\emph{Self-awareness}] Does being a mindreader entail being able, sometimes, to identify one's own mental states and actions? 
%
\item [\emph{Interaction}] How is mindreading involved in joint action?  
%
\item [\emph{Social Grounding}]  In what ways (if any) could mindreading, or its development or evolution, depend on abilities to engage in joint action?  
%
\end{itemize}

%
%My aim is to introduce research on philosophical topics likely to be useful to cognitive scientists with interests in joint action or mindreading. 
%Three criteria guide the selection of topics.
%The topics: are usually neglected (or misunderstood) by cognitive scientists;
% might inform experimental research;
%and
% linked to experimental research usually neglected (or misunderstood) by philosophers.
%

%\section{False Beliefs in the Theory of Mind}
%For an alternative way to get a feel for the aims of this course, 
%here is a list of claims---in no particular order---that will be examined systematically:
%
%\begin{enumerate}
%%
%\item There just two main ways of describing and explaining things: as mindless or as having propositional attitudes \citep[p.\ 697]{Davidson:2003bw}.
%%
%\item False belief tasks are an acid test for metarepresentation (see Bennett, Dennett and Harman commentaries on \citealp{premack_does_1978}).
%%
%\item Representing perception, intention, knowledge and ignorance is less cognitively or conceptually demanding than representing belief (perhaps because it doesn't involve having to coordinate representations of inconsistent propositions).
%Also, there could be mindreaders who can represent knowledge states but not beliefs \citep[][p.\ 191]{Call:2008di}.
%%`chimpanzees understand … intentions … perception and knowledge … Moreover, they understand how these psychological states work together to produce intentional action.' \citep[][p.\ 191]{Call:2008di}.
%%
%\item The function of mindreading is prediction and retrodiction: normativity and objectivity are irrelevant to understanding its development, and its cognitive and neurological bases.
%%
%\item Goals are intentions \citep{Fogassi:2005nf}.
%%
%\item Attribution of false beliefs is either automatic or not automatic; similarly for: modular, innate, and present by the second year of life \citep[p.\ 116]{Baillargeon:gx}.
%%
%\item For theoretical purposes, mindreaders can be thought of as mere observers; the possibility of social interaction can be ignored.  
%So a purely passive mindreader observing from behind a one-way mirror
%is on a par with
%a mindreader who, actually or apparently, could interact with those she seeks to interpret in this sense:
%in principle the same evidence could be available to each, and each can exploit the routes to knowledge in moving from evidence to ascriptions of thought and action \citep{Davidson:1973jx,Dennett:1987sf,lewis:1974ri}.
%%
%\item Abilities to engage in joint action depend on abilities to attribute intention, and knowledge or belief, to others.
%\end{enumerate}



\section{Provisional schedule}

Most classes will take the form of a lecture with questions and discussion time. 
There are also four afternoon sessions in which we'll discuss key papers.
See table \vref{table:schedule} for a provisional schedule. 
The schedule may change depending on group discussion and research interests.

{
	%increase space between rows
	\renewcommand{\arraystretch}{1.5}
\begin{table}[htbp]
\begin{center}
\footnotesize	%shrink for better spacing
\begin{tabular*}{1\textwidth}{ l l m{0.80\textwidth} } 

\toprule

1. & sept 12  
	&  \textit{Introduction: Some Questions about Mindreading and Joint Action}
\\  2. & sept 19  
	& \textit{What Are Mental States?}
		\newline Reading: \citet[§§1.1--1.3, 3.1--3.4, 4.1]{Jeffrey:1983oe}, \citet[§1]{fitch:2009_singular}
\\ &   sept 26 & [no class]
\\ 3. & oct 3 
		& \textit{Tracking, Measuring and Representing Beliefs}
			\newline  Reading: \citet{matthews:1994_measure}, \citet{kovacs_social_2010}
\\  4. & oct 10 
	&  \textit{What is Core Knowledge (or Modularity)?}
		%this is where I can do the paradox about the ages]
		\newline Reading: \citet{Fodor:1983dg,Fodor:2000cj,Baillargeon:gx,Wellman:2001lz}
		\newline Discussion: {\citet{Sugden:2000mw}}
\\ & oct 14 & [no class]
\\ 5. & oct 24 
	& 	%\textit{Radical Interpretation}
		%\newline Reading: \citet{Davidson:1985qg,Davidson:1973jx,Davidson:1980xp,Davidson:1990du}
		\textit{Actions, Intentions and Goals}
		\newline Reading: \citet{Davidson:1971fz,Davidson:1978hy,Bratman:1985fk,bratman:2000_valuing} 
		\newline Discussion:  \sout{\citet{matthews:1994_measure}} \citep{shah:2005_doxastic}
\\ 6. & oct 31 
	& \textit{Goal Ascription: the Teleological Stance and Motor Awareness}
		\newline Reading: \citet{Millikan:1989cd,Millikan:1993_behaviour,Millikan:1993_green,Gergely:1995sq,Csibra:2003kp,Fogassi:2005nf}
			%*Bratman What is Intention? (hard to source)
		\newline Discussion: \citet{Davidson:1973jx}
\\ & nov 7 & [no class]
\\ 7. & nov 14 
	& \textit{What Is Joint Action?}
		\newline Reading: \citet{Bratman:1992mi,Bratman:1993je,ludwig_collective_2007,Searle:1990em,carpenter:2009_howjoint}
		\newline Discussion: \citet{Bratman:1984jr}
\\ 8. & nov 21 
	&  \textit{Shared Intention and Motor Representation in Joint Action}
		\newline Reading: \citet{Knoblich:2008hy,kourtis:2010_favoritism}
\\ & nov 28 & [no class]
\\ 9. & dec 5 
	& \textit{Interacting Mindreaders}
	%[was planning to do Interacting Mindreaders but need to show some results (and will have done Interacting Mindreaders at the CEU colloq.]
		\newline Reading: \citet{Csibra:1998cx,Csibra:2009xr,leekam_adults_2010}
\\
%
\bottomrule
%
\end{tabular*}
\caption{Provisional schedule}
\label{table:schedule}
\end{center}	%careful -- position of this affects distance between table and caption(!)
\end{table}
}



\section{Method of evaluation}

Students may be asked to prepare one or more short (5--10 minute) presentations to introduce a discussion sessions. 
Presentations will not be graded nor contribute to any overall mark. 

Students may submit a short midterm paper of no more than 3000 words (fewer is better).
Midterm papers will not contribute to any overall mark.   
Midterm papers will receive feedback some feedback (a paragraph or so) but will not receive grades.

Students should submit a short term paper.  
The topic of each paper should ideally be agreed in advance; alternatively term papers may answer a question chosen from the list of questions below. 
Term papers may not substantially overlap with midterm papers where any individual is an author of both.


\section{Sample essay questions}
In addition to those below, also consider questions from the titles of lectures in table \vref{table:schedule}.
%
\begin{enumerate}
\item Are there limits on the behaviour that can be modelled using simple forms of decision theory \citep[such as the version presented in][]{Jeffrey:1983oe}?  You may choose to answer with respect to one of \citet{Sugden:2000mw} or \citet{bratman:2000_valuing}.
\item How, if at all, can we distinguish different kinds of mindreading?  If you provide a distinction, discuss an application of it.
\item Which events are actions?
\item What is the relation between a goal and an action when the action is directed to the goal?
\item What could someone represent that would enable her to track others' desires?
\item What could count as evidence that a mindreader was ascribing intentions to other individuals?  You might relate your answer one or more of the following: \citet{fogassi_mirror_2007,Dasser:1989qw,astington:2001_paradox,malle:2001_distinction}.
\item `The concept of a joint action as such is just that of an event of which there are multiple agents' \citep[p.\ 366]{ludwig_collective_2007}.  First explain and then evaluate this claim.
\item Does joint action necessarily involve mindreading?
\end{enumerate}


\section{Deadlines for submitting papers}

\subsection{Midterm papers}
Midterm papers should be submitted by 9 am on Monday 5th November.  Mindterm papers should be emailed directly to me (Butterfill).  Late midterm papers will not be read without prior agreement.  Midterm papers will be returned with feedback by Wednesday November 14, 2012 (unless there are very many).  

\subsection{Term papers}
The deadline for submitting term papers is 9 am on January 7, 2012. The grades will be returned by the instructor by January 21, 2013 together with some feedback (a paragraph or so).



\section{Reading and Sources}

(See the provisional schedule in table \vref{table:schedule}.)

{
	\def\section*#1{}	%remove section heading
	\bibliography{$HOME/endnote/phd_biblio}
}









\end{document}